Harnessing the cloud to understand light: A whitepaper detailing the \MaxwellFDS core solver

### 2013-03-28 thesis/chapter4.tex
Put together papers.

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
\usepackage{opex3}
\usepackage{amsmath,amssymb}

\newcommand{\myfig}[2]{
    \begin{figure}[!h]
    \begin{centering}
    \includegraphics[width=0.8\textwidth]{#1}
    \caption{#2}\label{#1}
    \end{centering}
    \end{figure}
}

\newcommand{\Eq}[1]{Eq.~\eqref{#1}}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}
\newcommand{\eq}[1]{eq.~\eqref{#1}}
\newcommand{\fig}[1]{fig.~\ref{#1}}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}
\newcommand{\BEAS}{\begin{eqnarray}}
\newcommand{\EEAS}{\end{eqnarray}}
% \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
% \newcommand{\EEAS}{\end{IEEEeqnarray}}
\newcommand{\BSA}{\begin{subequations}\begin{align}}
\newcommand{\ESA}{\end{align}\end{subequations}}
\newcommand{\BE}{\begin{equation*}}
\newcommand{\EE}{\end{equation*}}
\newcommand{\BIT}{\begin{itemize}}
\newcommand{\EIT}{\end{itemize}}

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.} }

\DeclareMathOperator*{\minimize}{\text{minimize}\quad}
\newcommand{\subto}{\text{subject to}\quad}
\newcommand{\T}{^\dagger}

\newcommand{\ones}{\mathbf 1}
\newcommand{\reals}{{\mbox{\bf R}}}
\newcommand{\comps}{{\mbox{\bf C}}}
\newcommand{\integers}{{\mbox{\bf Z}}}
\newcommand{\symm}{{\mbox{\bf S}}}  % symmetric matrices

\newcommand{\nullspace}{{\mathcal N}}
\newcommand{\range}{{\mathcal R}}
\newcommand{\Rank}{\mathop{\bf Rank}}
\newcommand{\Tr}{\mathop{\bf Tr}}
\newcommand{\diag}{\mathop{\bf diag}}
\newcommand{\lambdamax}{{\lambda_{\rm max}}}
\newcommand{\lambdamin}{\lambda_{\rm min}}

\newcommand{\Expect}{\mathop{\bf E{}}}
\newcommand{\Prob}{\mathop{\bf Prob}}
\newcommand{\Co}{{\mathop {\bf Co}}} % convex hull
\newcommand{\dist}{\mathop{\bf dist{}}}
\newcommand{\argmin}{\mathop{\rm argmin}}
\newcommand{\argmax}{\mathop{\rm argmax}}
\newcommand{\epi}{\mathop{\bf epi}} % epigraph
\newcommand{\Vol}{\mathop{\bf vol}}
\newcommand{\dom}{\mathop{\bf dom}} % domain
\newcommand{\intr}{\mathop{\bf int}}

\begin{document}

\title{Nanophotonic Computational Design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

\begin{abstract}
In contrast to designing nanophotonic devices 
    by tuning a handful of device parameters, 
    we have developed a computational method 
    which utilizes the full parameter space to design linear nanophotonic devices.
We show that our method may indeed be capable of designing 
    any linear nanophotonic device by demonstrating designed structures which
    are fully three-dimensional and multi-modal,
    exhibit novel functionality,
    have very compact footprints,
    exhibit high efficiency, and
    are manufacturable.
In addition, we also demonstrate the ability to produce structures
    which are strongly robust to wavelength and temperature shift,
    as well as fabrication error.
Critically, we show that our method 
    does not require the user to be a nanophotonic expert or 
    to perform any manual tuning. 
Instead, we are able to design devices 
    solely based on the user's desired performance specification for the device.
\end{abstract}
\ocis{230.75370, 130.3990.}

\begin{thebibliography}{99}
\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012)
\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
%     nanophotonic circuits,''
%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
%     ``Active control of slow light on a chip with photonic crystal waveguides,''
%     Nature \textbf{438}, 65-69 (2005).
% \bibitem{slotfocus} M. Lipson, 
%     ``Guiding, modulating, and emitting light on 
%     silicon-challenges and opportunities,'' 
%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
%     C. Lagahe, and R. Baets, 
%     ``Electrically pumped InP-based microdisk lasers integrated with a 
%     nanophotonic silicon-on-insulator waveguide circuit,'' 
%     Opt. Express \textbf{15}, 6744-6749 (2007).
% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
%     ``Nanometre-scale germanium photodetector enhanced by a 
%     near-infrared dipole antenna,'' 
%     Nature Photonics \textbf{2}, 226-229 (2008).
% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
% %     ``Nanotaper for compact mode conversion,'' 
% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
% %     ``Adiabatic theorem and continuous coupled-mode theory for 
% %     efficient taper transitions in photonic crystals,''
% %     Phys. Rev. E \textbf{66}, 066608 (2002)
% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
% %     ``Robust topology optimization of photonic crystal waveguides with 
% %     tailored dispersion properties.'' 
% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
% %     \emph{Convex Optimization} 
% %     (Cambridge University Press, 2004)
% \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
%     ``Inverse design of a three-dimensional nanophotonic resonator,''
%     Opt. Express \textbf{19}, 10563-10750 (2011). 
% \bibitem{veronis} G. Veronis, and S. Fan, 
%     ``Theoretical investigations of compact couplers between dielectric slab 
%     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
%     Opt. Express \textbf{15}, 1211-1221 (2007).
% \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
%     ``Efficient light coupling between dielectric slot waveguide and plasmonic
%     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
% \bibitem{code} \url{www.github.com/JesseLu/objective-first}
\end{thebibliography}

\section{Introduction}
Currently, almost all nanophotonic components are designed 
    by hand-tuning a small number of parameters 
    (e.g. waveguide widths and gaps, hole and ring sizes).
However, the realization of 
    increasingly complex, dense, and robust on-chip optical networks
    will require utilizing increasing numbers of parameters
    when designing nanophotonic components.

@@

This work has been supported by the 
    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
\end{document}

>>>>

% \documentclass[letterpaper,10pt]{article}
% \usepackage{graphicx}
% \usepackage{opex3}
% \usepackage{amsmath,amssymb}
% 
% 
% \newcommand{\myfig}[2]{
%     \begin{figure}[!h]
%     \begin{centering}
%     \includegraphics[width=0.8\textwidth]{fig/#1}
%     \caption{#2}\label{#1}
%     \end{centering}
%     \end{figure}
% }
% 
% \newcommand{\Eq}[1]{Eq.~\eqref{#1}}
% \newcommand{\Fig}[1]{Fig.~\ref{#1}}
% \newcommand{\eq}[1]{eq.~\eqref{#1}}
% \newcommand{\fig}[1]{fig.~\ref{#1}}
% \newcommand{\BI}{\begin{itemize}\item}
% \newcommand{\I}{\item}
% \newcommand{\EI}{\end{itemize}}
% \newcommand{\BEAS}{\begin{eqnarray}}
% \newcommand{\EEAS}{\end{eqnarray}}
% % \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
% % \newcommand{\EEAS}{\end{IEEEeqnarray}}
% \newcommand{\BSA}{\begin{subequations}\begin{align}}
% \newcommand{\ESA}{\end{align}\end{subequations}}
% \newcommand{\BE}{\begin{equation*}}
% \newcommand{\EE}{\end{equation*}}
% \newcommand{\BIT}{\begin{itemize}}
% \newcommand{\EIT}{\end{itemize}}
% 
% \newcommand{\eg}{{\it e.g.}}
% \newcommand{\ie}{{\it i.e.} }
% 
% \DeclareMathOperator*{\minimize}{\text{minimize}\quad}
% \newcommand{\subto}{\text{subject to}\quad}
% \newcommand{\T}{^\dagger}
% 
% 
% \newcommand{\ones}{\mathbf 1}
% \newcommand{\reals}{{\mbox{\bf R}}}
% \newcommand{\comps}{{\mbox{\bf C}}}
% \newcommand{\integers}{{\mbox{\bf Z}}}
% \newcommand{\symm}{{\mbox{\bf S}}}  % symmetric matrices
% 
% \newcommand{\nullspace}{{\mathcal N}}
% \newcommand{\range}{{\mathcal R}}
% \newcommand{\Rank}{\mathop{\bf Rank}}
% \newcommand{\Tr}{\mathop{\bf Tr}}
% \newcommand{\diag}{\mathop{\bf diag}}
% \newcommand{\lambdamax}{{\lambda_{\rm max}}}
% \newcommand{\lambdamin}{\lambda_{\rm min}}
% 
% \newcommand{\Expect}{\mathop{\bf E{}}}
% \newcommand{\Prob}{\mathop{\bf Prob}}
% \newcommand{\Co}{{\mathop {\bf Co}}} % convex hull
% \newcommand{\dist}{\mathop{\bf dist{}}}
% \newcommand{\argmin}{\mathop{\rm argmin}}
% \newcommand{\argmax}{\mathop{\rm argmax}}
% \newcommand{\epi}{\mathop{\bf epi}} % epigraph
% \newcommand{\Vol}{\mathop{\bf vol}}
% \newcommand{\dom}{\mathop{\bf dom}} % domain
% \newcommand{\intr}{\mathop{\bf int}}
% 
% \begin{document}
% 
% \title{Nanophotonic Computational Design}
% \author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
% \address{Stanford University, Stanford, California, USA.}
% \email{jesselu@stanford.edu}
% 
% \begin{abstract}
% In contrast to designing nanophotonic devices 
%     by tuning a handful of device parameters, 
%     we have developed a computational method 
%     which utilizes the full parameter space to design linear nanophotonic devices.
% We show that our method may indeed be capable of designing 
%     any linear nanophotonic device by demonstrating designed structures which
%     are fully three-dimensional and multi-modal,
%     exhibit novel functionality,
%     have very compact footprints,
%     exhibit high efficiency, and
%     are manufacturable.
% In addition, we also demonstrate the ability to produce structures
%     which are strongly robust to wavelength and temperature shift,
%     as well as fabrication error.
% Critically, we show that our method 
%     does not require the user to be a nanophotonic expert or 
%     to perform any manual tuning. 
% Instead, we are able to design devices 
%     solely based on the user's desired performance specification for the device.
% \end{abstract}
% \ocis{230.75370, 130.3990.}
% 
% \begin{thebibliography}{99}
% \bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
%     Opt. Express \textbf{20}, 7221-7236 (2012)
% \bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
%     ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
%     Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
% \bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
%     J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
% \bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
% \bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
%     ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
% \bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
%     ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
%     J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
% % \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
% %     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
% %     nanophotonic circuits,''
% %     Opt. Lett. \textbf{35}, 1290-1292 (2010).
% % \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
% %     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
% %     Opt. Lett. \textbf{26}, 1888-1890 (2001).
% % \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
% %     ``Active control of slow light on a chip with photonic crystal waveguides,''
% %     Nature \textbf{438}, 65-69 (2005).
% % \bibitem{slotfocus} M. Lipson, 
% %     ``Guiding, modulating, and emitting light on 
% %     silicon-challenges and opportunities,'' 
% %     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
% % \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
% %     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
% %     C. Lagahe, and R. Baets, 
% %     ``Electrically pumped InP-based microdisk lasers integrated with a 
% %     nanophotonic silicon-on-insulator waveguide circuit,'' 
% %     Opt. Express \textbf{15}, 6744-6749 (2007).
% % \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
% %     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
% %     ``Nanometre-scale germanium photodetector enhanced by a 
% %     near-infrared dipole antenna,'' 
% %     Nature Photonics \textbf{2}, 226-229 (2008).
% % % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
% % %     ``Nanotaper for compact mode conversion,'' 
% % %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% % % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
% % %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
% % %     ``Adiabatic theorem and continuous coupled-mode theory for 
% % %     efficient taper transitions in photonic crystals,''
% % %     Phys. Rev. E \textbf{66}, 066608 (2002)
% % % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
% % %     ``Robust topology optimization of photonic crystal waveguides with 
% % %     tailored dispersion properties.'' 
% % %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% % % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
% % %     \emph{Convex Optimization} 
% % %     (Cambridge University Press, 2004)
% % \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
% %     ``Inverse design of a three-dimensional nanophotonic resonator,''
% %     Opt. Express \textbf{19}, 10563-10750 (2011). 
% % \bibitem{veronis} G. Veronis, and S. Fan, 
% %     ``Theoretical investigations of compact couplers between dielectric slab 
% %     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
% %     Opt. Express \textbf{15}, 1211-1221 (2007).
% % \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
% %     ``Efficient light coupling between dielectric slot waveguide and plasmonic
% %     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
% % \bibitem{code} \url{www.github.com/JesseLu/objective-first}
% \end{thebibliography}
\chapter{Final Result}
\section{Introduction}
Currently, almost all nanophotonic components are designed 
    by hand-tuning a small number of parameters 
    (e.g. waveguide widths and gaps, hole and ring sizes).
However, the realization of 
    increasingly complex, dense, and robust on-chip optical networks
    will require utilizing increasing numbers of parameters
    when designing nanophotonic components.

@@

This work has been supported by the 
    AFOSR MURI for Complex and Robust On-chip Nanophotonics 
    (Dr. Gernot Pomrenke), grant number FA9550-09-1-0704.
% \end{document}
